Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
added histogram that is a percent match for characterstics that were part of one's job.

  Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared. 
  In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.

@@

>>>>

  Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared. 
  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job). Figure ?? shows the distribution of the proportion of matches by person.

  In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.

@@

```
```{r match percents by person}
#rc1 to rc 84

data$match_rc_by_person <- rowSums(data[495:578], na.rm = TRUE)

data$match_rc_by_person_NAs <- rowSums(is.na(data[495:578]))

#This should be matches divided by 84 items minus nas
data$percent_match_total_person <- (data$match_rc_by_person/(84 - data$match_rc_by_person_NAs))
head(data$percent_match_total_person)

hist(data$percent_match_total_person)
```
